---
title: "Use of correctCounts for assigning multiply-mapped-reads"
author: "Douglas Wu"
date: "May 14, 2016"
output: html_document
---

This package contains only one function *correctCounts* as to assign multiply-mapped-reads to the most abundant gene that it mapped to.

```{r warning=F}
library(correctMultiCount)

data(baseCount)
data(multiCount)

head(baseCount)
head(multiCount)
```

Noted that this function needed to two data frames with the exact column names as shown here.

* baseCount dataframe needed to have 2 columns named as 
  1. id 
  2. count
* multiCount dataframe needed to have 2 columns named as
  1. fragment_id         
  2. gene_id

``` {r}
df <- correctCounts(baseCount,multiCount)
head(df)
```


Now, lets check if it works as we thought.
```{r warning=F, message=F}
library(dplyr)
compareDF <- df %>% 
  setNames(c('id','newCount')) %>%
  inner_join(baseCount) %>%   # merge the old and new count dataframe
  tbl_df
```

And find out the fragments that mapped to at least two locus

```{r}
multiCount %>% 
  group_by(fragment_id) %>% 
  summarize(mapped_location_count = n()) %>% 
  filter(mapped_location_count > 1) %>%
  arrange(-mapped_location_count) %>%
  tbl_df
```

Lets check the third fragment
```{r}
fragment = multiCount %>%
  filter(fragment_id=='NS500358:89:HJWK2BGXX:1:11101:22227:18777') %>%
  tbl_df
head(fragment)

fragment_mapped_gene <- fragment$gene_id
compareDF %>%
  filter(id %in% fragment_mapped_gene)
```

So here you see, the multiply-mapped gene is assign to the only gene locus that originally has count.
